### 2020-05-18 writeup/proof_transfer_ex.tex
proof reduce date ratio

\subsection{Proof of Proposition \ref{prop_data_size}}\label{app_proof_data}

Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
\be\label{pos1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
otherwise if
\be\label{neg1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

@@

The second statement can be proved in a similar way. Suppose $c_1 \ge 110$ and $pd^2 > \frac{3\sigma^2}{2(c_2-1)}$. If $c_1 > \frac{(c_2-2) \sigma^2}{2(c_2 - 1) pd^2/3 - \sigma^2}$, we have
\begin{align*}
 pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac{2}{3} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  >\sigma^2, 
 \end{align*}
 where in the first step we used that 
 $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac23$$
 for $c_1 \ge 110$. This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. On the other hand, if $100\le c_1 \le \frac{(c_2-2) \sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then we have 
 \begin{align*}
 pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac{3}{2} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  < \sigma^2, 
 \end{align*}
 where in the first step we used that 
 $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac32$$
 for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.

@@

>>>>

\subsection{Proof of Proposition \ref{prop_data_size} and Proposition \ref{prop_data_efficiency}}\label{app_proof_data}

\begin{proof}[Proof of Proposition \ref{prop_data_size}]
Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
\be\label{pos1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
otherwise if
\be\label{neg1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

@@

The second statement can be proved in a similar way. Suppose $c_1 \ge 110$ and $pd^2 > \frac{3\sigma^2}{2(c_2-1)}$. If $c_1 > \frac{(c_2-2) \sigma^2}{2(c_2 - 1) pd^2/3 - \sigma^2}$, we have
\begin{align*}
 pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac{2}{3} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  >\sigma^2, 
 \end{align*}
 where in the first step we used that 
 $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac23$$
 for $c_1 \ge 110$. This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. On the other hand, if $100\le c_1 \le \frac{(c_2-2) \sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then we have 
 \begin{align*}
 pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac{3}{2} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  < \sigma^2, 
 \end{align*}
 where in the first step we used that 
 $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac32$$
 for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
 \end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=n_2$. In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}, and by symmetry it suffices to focus on one of tasks, say task 2. Using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, we have that whp,
\be\label{reduceproof1}
\begin{split}
\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{2\al c - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(2)}_{\beta},
\end{split}
\ee
where $ \Delta^{(2)}_{\beta}$ satisfies 
\be \nonumber
\bigbrace{1 - \sqrt{\frac{1}{\al c}}}^4 \le \Delta^{(2)}_{\beta} /  \left( pd^2 \cdot \frac{2\al^3 c^3}{(2\al c-1)^3}+ \bigo{p^{1/2+\e}d^2}\right) \le \bigbrace{1 + \sqrt{\frac{1}{\al c}}}^4. 
\ee
On the other hand, using Lemma \ref{lem_minv}, we have whp
\be\label{reduceproof2} 
\te_2(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{c-1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right).
\ee
Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.

Now for $c\ge 200$ and $\al \ge 1/2$, we have whp
\be\label{reduceproof3} \te_2(\hat \beta(\al)) < \sigma^2 \frac{1}{2\al c - 1}+  \frac38 pd^2  \ee
for large enough $p$. Moreover, if 
$$\al \ge \al_0:=\frac{1}{2c} + \left(2-\frac{3}{4}c \cdot \frac{pd^2}{\sigma^2} \right)^{-1},$$
we can check from \eqref{reduceproof3} that $\te_2(\hat \beta(\al))  < \te_2(\hat{\beta}_t^{\STL}) $. By symmetry, we also have $\te_1(\hat \beta(\al))  < \te_1(\hat{\beta}_t^{\STL}) $. Thus we conclude that 
$$\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$$
for $\al\ge \al_0$, which shows that $\al^*\le \al_0$.
\end{proof}

### 2020-05-18 writeup/transfer.tex
sec 3.3
proof reduce date ratio

\begin{proposition}\label{prop_data_efficiency}
	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c > ??$ and $d^2 \le {2\sigma^2} /{(p c)}$.
	Then the data efficiency ratio is equal to $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - p d^2 c / 2}$.
\end{proposition}
Note that we have stated the result assuming that $c_1 = c_2$.
Similar results can also be obtained when they are different.
We omit the details.
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

@@

\begin{proposition}\label{prop_covariate}
	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$.
	As a parameter of $M \in \cS_{\mu}$, we have that $\te(\hat{\beta}_t^{\MTL})$ is minimized when $M = \mu\id$.
\end{proposition}

>>>>

\begin{proposition}\label{prop_data_efficiency}
	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c \ge 200$ and $d^2 < {8\sigma^2} /{(3p c)}$.
	Then the data efficiency ratio is at most $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 c / 4}$.
\end{proposition}
Note that we have stated the result assuming that $c_1 = c_2$.
Similar results can also be obtained when they are different.
We omit the details.
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

@@

\begin{proposition}\label{prop_covariate}
	In the setting of Example \ref{ex_basic}, assume that $d^2 < \sigma^2 / (c_1 p)$ and $c_1 > ??$.
	As a parameter of $M \in \cS_{\mu}$, we have that $\te(\hat{\beta}_t^{\MTL})$ is minimized when $M = \mu\id$.
\end{proposition}
